The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-11 Writeup/paper_v3.tex
Concerns and figure references

We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
indices of the stellar mass-selected samples (\s$3$) are
systematically greater than those of the luminosity selected samples
(\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higher? No need to hedge.}) not
surprising that it has a higher median \sersic $n$.  Finally, even for
the stellar mass-selected sample there is some sign of redshift
evolution.  The sign of this evolution is as expected, with lower
\sersic $n$ and $B/T$ for higher redshift samples, which should have a
higher fraction of disk and irregular galaxies and fewer galaxies with
bulge-like morphology.

@@

The intrinsic ellipticity distribution plays a role in nearly all
shear estimators.  In some, the role is explicit: for example, LensFit
\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
and the methods presented by \cite{2014MNRAS.438.1880B} require
accurate intrinsic ellipticity distributions as inputs, and
uncertainty in the distribution was one of the important sources of
systematic uncertainty in the CFHTLenS weak lensing results
\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  In others, the role
is implicit.  For example, the re-Gaussianization method and several
other moment-based methods require calculation of a shear responsivity
\citep{BJ02,HS03} that describes how the galaxy population overall
responds to a shear, based on its intrinsic ellipticity distribution.
The responsivity can be calculated based on the observed shape
distribution, assuming that the uncertainties in the shears are known
enough that their contribution to that distribution can be removed.
If a simulated sample in some redshift slice has a different intrinsic
ellipticity distribution and therefore responsivity, it could lead to
incorrect conclusions about shear calibration.  The responsivity
scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
RMS ellipticity at the level of 0.01 (\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.}) would become fractional shear
errors of
\begin{equation}
\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
\end{equation}
In the context of upcoming lensing surveys that seek to constrain
shears to the per cent level or better, a systematic error of this
magnitude in shear calibration is quite serious.

>>>>

We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
indices of the stellar mass-selected samples (\s$3$) are
systematically greater than those of the luminosity selected samples
(\s$1$, \s$2$).  We saw that \s3 is the smallest sample, and thus is
likely limited to higher mass galaxies overall.  It is therefore (\claire{Can't you show the masses are higher? No need to hedge.} \arun{I am not sure what you want me to show here.}) not
surprising that it has a higher median \sersic $n$.  Finally, even for
the stellar mass-selected sample there is some sign of redshift
evolution.  The sign of this evolution is as expected, with lower
\sersic $n$ and $B/T$ for higher redshift samples, which should have a
higher fraction of disk and irregular galaxies and fewer galaxies with
bulge-like morphology.

@@

The intrinsic ellipticity distribution plays a role in nearly all
shear estimators.  In some, the role is explicit: for example, LensFit
\citep{2007MNRAS.382..315M,2008MNRAS.390..149K,2013MNRAS.429.2858M}
and the methods presented by \cite{2014MNRAS.438.1880B} require
accurate intrinsic ellipticity distributions as inputs, and
uncertainty in the distribution was one of the important sources of
systematic uncertainty in the CFHTLenS weak lensing results
\citep{2013MNRAS.432.2433H,2013MNRAS.429.2858M}.  In others, the role
is implicit.  For example, the re-Gaussianization method and several
other moment-based methods require calculation of a shear responsivity
\citep{BJ02,HS03} that describes how the galaxy population overall
responds to a shear, based on its intrinsic ellipticity distribution.
The responsivity can be calculated based on the observed shape
distribution, assuming that the uncertainties in the shears are known
enough that their contribution to that distribution can be removed.
If a simulated sample in some redshift slice has a different intrinsic
ellipticity distribution and therefore responsivity, it could lead to
incorrect conclusions about shear calibration.  The responsivity
scales roughly like $1-e_\text{RMS}^2$, which means that deviations in
RMS ellipticity at the level of 0.01 (Figs.~\ref{fig:rms_ellip} and~\ref{fig:rms_ellip_momentbased})(\claire{That's the level you find, correct?} \rachel{Yes, perhaps we should reference a figure when we mention this so that it's clear where 0.01 comes from.} \arun{Referring both figures is fine?}) would become fractional shear
errors of
\begin{equation}
\frac{\Delta\gamma}{\gamma} \approx \frac{2 e_\text{RMS} \Delta
  e_\text{RMS} }{1-e_\text{RMS}^2} \approx 0.01.
\end{equation}
In the context of upcoming lensing surveys that seek to constrain
shears to the per cent level or better, a systematic error of this
magnitude in shear calibration is quite serious.
